Accelerated signal-and-noise orthogonalization

### 2022-01-05 orthoa/paper.tex
Wed Jan  5 17:26:27 CST 2022

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/c}
   \label{fig:c}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/n}
   \label{fig:n}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cn}
   \label{fig:cn}}\\
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cfx}
   \label{fig:cfx}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cfx2}
   \label{fig:cfx2}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cfx22}
   \label{fig:cfx22}}\\  
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cdifffx}
   \label{fig:cdifffx}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cdifffx2}
   \label{fig:cdifffx2}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cdifffx22}
   \label{fig:cdifffx22}}
\caption{Comparison of using the local-orthogonalization-based random noise attenuation approach for denoising test before and after. (a) Clean section. (b) Random noise section. (c) Noisy section (S/N=-0.75 dB). (d) Denoised result using $f$-$x$ deconvolution (S/N=9.21 dB). (e) Denoised result using the traditional orthogonalization method (S/N=10.99 dB). (f) Denoised result using the proposed method (S/N=10.40 dB). (g) Noise section using $f$-$x$ deconvolution. (h) Noise section using traditional orthogonalization method. (i) Noise section using the proposed method.}
\label{fig:c,n,cn,cfx,cfx2,cfx22,cdifffx,cdifffx2,cdifffx22}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/csimi-difffx}
   \label{fig:csimi-difffx}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/csimi-difffx2}
   \label{fig:csimi-difffx2}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/csimi-difffx22}
   \label{fig:csimi-difffx22}}
\caption{(a) Local similarity map using FX method. (b) Local similarity using the traditional orthogonalization method. (c) Local similarity using the proposed accelerated orthogonalization method.}
\label{fig:csimi-difffx,csimi-difffx2,csimi-difffx22}
\end{figure}

@@

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huo}
   \label{fig:huo}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huo-noise}
   \label{fig:huo-noise}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos}
   \label{fig:huos}}\\
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-mf}
   \label{fig:huos-mf}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-ortho}
   \label{fig:huos-ortho}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-ortho2}
   \label{fig:huos-ortho2}}\\  
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huosdiff-mf}
   \label{fig:huosdiff-mf}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huosdiff-ortho}
   \label{fig:huosdiff-ortho}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huosdiff-ortho2}
   \label{fig:huosdiff-ortho2}}
\caption{Comparison of using the local-orthogonalization-based blending noise attenuation approach for denoising test before and after. (a) Clean section. (b) Blending noise section. (c) Noisy section (S/N=0.78 dB). (d) Denoised result using median filtering (S/N=10.91 dB). (e) Denoised result using the traditional orthogonalization method (S/N=11.35 dB). (f) Denoised result using the proposed method (S/N=12.14 dB). (g) Noise section using median filtering. (h) Noise section using traditional orthogonalization method. (i) Noise section using the proposed method.}
\label{fig:huo,huo-noise,huos,huos-mf,huos-ortho,huos-ortho2,huosdiff-mf,huosdiff-ortho,huosdiff-ortho2}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-simi}
   \label{fig:huos-simi}} 
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-simi-ortho}
   \label{fig:huos-simi-ortho}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-simi-ortho2}
   \label{fig:huos-simi-ortho2}}
\caption{(a) Local similarity map using median filtering. (b) Local similarity using the traditional orthogonalization method. (c) Local similarity using the proposed accelerated orthogonalization method.}
\label{fig:huos-simi,huos-simi-ortho,huos-simi-ortho2}
\end{figure}

@@

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-fx}
   \label{fig:pp-fx}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-ortho}
   \label{fig:pp-ortho}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-ortho2}
   \label{fig:pp-ortho2}}\\
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/ppdiff-fx0}
   \label{fig:ppdiff-fx0}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/ppdiff-ortho0}
   \label{fig:ppdiff-ortho0}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/ppdiff-ortho20}
   \label{fig:ppdiff-ortho20}}\\  
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-simi}
   \label{fig:pp-simi}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-simi-ortho}
   \label{fig:pp-simi-ortho}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-simi-ortho2}
   \label{fig:pp-simi-ortho2}}
\caption{Denoising comparison. (a) Denoised data using $f$-$x$ deconvolution. (b) Denoised data using the traditional local orthogonalization. (c) Denoised data using the accelerated local orthogonalization. (d)-(f) Removed noise corresponding to (a)-(c), respectively. (g)-(i) Local similarity comparison corresponding to (a)-(c), respectively.}
\label{fig:pp-fx,pp-ortho,pp-ortho2,ppdiff-fx0,ppdiff-ortho0,ppdiff-ortho20,pp-simi,pp-simi-ortho,pp-simi-ortho2}
\end{figure}

@@

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.8\columnwidth]{rna/Fig/data0}
   \label{fig:data0}}\\
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-data-a}
   \label{fig:zoom-data-a}}
\subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-data-b}
   \label{fig:zoom-data-b}} 
\caption{Field data example. (a) Field data of the original scale. (b) Zoomed data corresponding to A. (c) Zoomed data corresponding to B.}
\label{fig:data0,zoom-data-a,zoom-data-b}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/npre0}
   \label{fig:npre0}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-ortho0}
   \label{fig:rna-ortho0}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-ortho20}
   \label{fig:rna-ortho20}}\\
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/nprediff0}
   \label{fig:nprediff0}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rnadiff-ortho0}
   \label{fig:rnadiff-ortho0}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rnadiff-ortho20}
   \label{fig:rnadiff-ortho20}}\\  
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-simi}
   \label{fig:rna-simi}}
\subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-simi-ortho}
   \label{fig:rna-simi-ortho}}
   \subfigure[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-simi-ortho2}
   \label{fig:rna-simi-ortho2}}
\caption{Denoising comparison. (a) Denoised data using $f$-$x$ regularized non-stationary autoregression. (b) Denoised data using the traditional local orthogonalization. (c) Denoised data using the accelerated local orthogonalization. (d)-(f) Removed noise corresponding to (a)-(c), respectively. (g)-(i) Local similarity comparison corresponding to (a)-(c), respectively.}
\label{fig:npre0,rna-ortho0,rna-ortho20,nprediff0,rnadiff-ortho0,rnadiff-ortho20,rna-simi,rna-simi-ortho,rna-simi-ortho2}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-npre-a}
   \label{fig:zoom-npre-a}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-npre-b}
   \label{fig:zoom-npre-b}}\\
\subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rna-ortho-a}
   \label{fig:zoom-rna-ortho-a}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rna-ortho2-b}
   \label{fig:zoom-rna-ortho-b}}\\
\subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rna-ortho2-a}
   \label{fig:zoom-rna-ortho2-a}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rna-ortho2-b}
   \label{fig:zoom-rna-ortho2-b}}\\  
\caption{Zoomed comparison of denoised sections. Left column: zoomed frame box A. Right column: zoomed frame box B.}
\label{fig:zoom-npre-a,zoom-npre-b,zoom-rna-ortho-a,zoom-rna-ortho-b,zoom-rna-ortho2-a,zoom-rna-ortho2-b}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rnadif-a}
   \label{fig:zoom-rnadif-a}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rnadif-b}
   \label{fig:zoom-rnadif-b}}\\
\subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-orthodif-a}
   \label{fig:zoom-orthodif-a}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-orthodif-b}
   \label{fig:zoom-orthodif-b}}\\
\subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-ortho2dif-a}
   \label{fig:zoom-ortho2dif-a}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-ortho2dif-b}
   \label{fig:zoom-ortho2dif-b}}\\  
\caption{Zoomed comparison of noise sections. Left column: zoomed frame box A. Right column: zoomed frame box B.}
\label{fig:zoom-rnadif-a,zoom-rnadif-b,zoom-orthodif-a,zoom-orthodif-b,zoom-ortho2dif-a,zoom-ortho2dif-b}
\end{figure}

@@

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/c}
   \label{fig:c}}
\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/cn}
   \label{fig:cn}}\\
\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/c-fx}
   \label{fig:c-fx}}
\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/c-fx-n0}
   \label{fig:c-fx-n0}}\\
\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/c-fxp}
   \label{fig:c-fxp}}
\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/c-fxp-n0}
   \label{fig:c-fxp-n0}}\\   
\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/c-fxortho}
   \label{fig:c-fxortho}}
\subfigure[]{\includegraphics[width=0.45\columnwidth]{linear/Fig/c-fxortho-n0}
   \label{fig:c-fxortho-n0}}\\    
\caption{\new{Comparison between the $f-x$ prediction method, $f-x$ projection method, and the hybrid $f-x$ prediction and orthogonalization method. First row: Clean and noisy data. Second row: denoised data and noise section using the $f-x$ prediction method.  Third row: denoised data and noise section using the $f-x$ projection method. Fourth row: denoised data and noise section using the hybrid method.}}
\label{fig:comp}
\end{figure}

@@

\bibliographystyle{IEEEtran}
\bibliography{ortho}

>>>>

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/c}
   \label{fig:c}}
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/n}
   \label{fig:n}}
\subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cn}
   \label{fig:cn}}\\
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cfx}
   \label{fig:cfx}}
\subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cfx2}
   \label{fig:cfx2}}
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cfx22}
   \label{fig:cfx22}}\\  
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cdifffx}
   \label{fig:cdifffx}}
\subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cdifffx2}
   \label{fig:cdifffx2}}
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/cdifffx22}
   \label{fig:cdifffx22}}
\caption{Comparison of using the local-orthogonalization-based random noise attenuation approach for denoising test before and after. (a) Clean section. (b) Random noise section. (c) Noisy section (S/N=-0.75 dB). (d) Denoised result using $f$-$x$ deconvolution (S/N=9.21 dB). (e) Denoised result using the traditional orthogonalization method (S/N=10.99 dB). (f) Denoised result using the proposed method (S/N=10.40 dB). (g) Noise section using $f$-$x$ deconvolution. (h) Noise section using traditional orthogonalization method. (i) Noise section using the proposed method.}
\label{fig:c,n,cn,cfx,cfx2,cfx22,cdifffx,cdifffx2,cdifffx22}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/csimi-difffx}
   \label{fig:csimi-difffx}}
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/csimi-difffx2}
   \label{fig:csimi-difffx2}}
\subfloat[]{\includegraphics[width=0.31\columnwidth]{complex/Fig/csimi-difffx22}
   \label{fig:csimi-difffx22}}
\caption{(a) Local similarity map using FX method. (b) Local similarity using the traditional orthogonalization method. (c) Local similarity using the proposed accelerated orthogonalization method.}
\label{fig:csimi-difffx,csimi-difffx2,csimi-difffx22}
\end{figure}

@@

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huo}
   \label{fig:huo}}
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huo-noise}
   \label{fig:huo-noise}}
\subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos}
   \label{fig:huos}}\\
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-mf}
   \label{fig:huos-mf}}
\subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-ortho}
   \label{fig:huos-ortho}}
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-ortho2}
   \label{fig:huos-ortho2}}\\  
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huosdiff-mf}
   \label{fig:huosdiff-mf}}
\subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huosdiff-ortho}
   \label{fig:huosdiff-ortho}}
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huosdiff-ortho2}
   \label{fig:huosdiff-ortho2}}
\caption{Comparison of using the local-orthogonalization-based blending noise attenuation approach for denoising test before and after. (a) Clean section. (b) Blending noise section. (c) Noisy section (S/N=0.78 dB). (d) Denoised result using median filtering (S/N=10.91 dB). (e) Denoised result using the traditional orthogonalization method (S/N=11.35 dB). (f) Denoised result using the proposed method (S/N=12.14 dB). (g) Noise section using median filtering. (h) Noise section using traditional orthogonalization method. (i) Noise section using the proposed method.}
\label{fig:huo,huo-noise,huos,huos-mf,huos-ortho,huos-ortho2,huosdiff-mf,huosdiff-ortho,huosdiff-ortho2}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-simi}
   \label{fig:huos-simi}} 
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-simi-ortho}
   \label{fig:huos-simi-ortho}}
\subfloat[]{\includegraphics[width=0.31\columnwidth]{csimul/Fig/huos-simi-ortho2}
   \label{fig:huos-simi-ortho2}}
\caption{(a) Local similarity map using median filtering. (b) Local similarity using the traditional orthogonalization method. (c) Local similarity using the proposed accelerated orthogonalization method.}
\label{fig:huos-simi,huos-simi-ortho,huos-simi-ortho2}
\end{figure}

@@

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-fx}
   \label{fig:pp-fx}}
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-ortho}
   \label{fig:pp-ortho}}
\subfloat[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-ortho2}
   \label{fig:pp-ortho2}}\\
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/ppdiff-fx0}
   \label{fig:ppdiff-fx0}}
\subfloat[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/ppdiff-ortho0}
   \label{fig:ppdiff-ortho0}}
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/ppdiff-ortho20}
   \label{fig:ppdiff-ortho20}}\\  
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-simi}
   \label{fig:pp-simi}}
\subfloat[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-simi-ortho}
   \label{fig:pp-simi-ortho}}
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{nine/Fig/pp-simi-ortho2}
   \label{fig:pp-simi-ortho2}}
\caption{Denoising comparison. (a) Denoised data using $f$-$x$ deconvolution. (b) Denoised data using the traditional local orthogonalization. (c) Denoised data using the accelerated local orthogonalization. (d)-(f) Removed noise corresponding to (a)-(c), respectively. (g)-(i) Local similarity comparison corresponding to (a)-(c), respectively.}
\label{fig:pp-fx,pp-ortho,pp-ortho2,ppdiff-fx0,ppdiff-ortho0,ppdiff-ortho20,pp-simi,pp-simi-ortho,pp-simi-ortho2}
\end{figure}

@@

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.8\columnwidth]{rna/Fig/data0}
   \label{fig:data0}}\\
   \subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-data-a}
   \label{fig:zoom-data-a}}
\subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-data-b}
   \label{fig:zoom-data-b}} 
\caption{Field data example. (a) Field data of the original scale. (b) Zoomed data corresponding to A. (c) Zoomed data corresponding to B.}
\label{fig:data0,zoom-data-a,zoom-data-b}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/npre0}
   \label{fig:npre0}}
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-ortho0}
   \label{fig:rna-ortho0}}
\subfloat[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-ortho20}
   \label{fig:rna-ortho20}}\\
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/nprediff0}
   \label{fig:nprediff0}}
\subfloat[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rnadiff-ortho0}
   \label{fig:rnadiff-ortho0}}
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rnadiff-ortho20}
   \label{fig:rnadiff-ortho20}}\\  
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-simi}
   \label{fig:rna-simi}}
\subfloat[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-simi-ortho}
   \label{fig:rna-simi-ortho}}
   \subfloat[]{\includegraphics[width=0.31\columnwidth]{rna/Fig/rna-simi-ortho2}
   \label{fig:rna-simi-ortho2}}
\caption{Denoising comparison. (a) Denoised data using $f$-$x$ regularized non-stationary autoregression. (b) Denoised data using the traditional local orthogonalization. (c) Denoised data using the accelerated local orthogonalization. (d)-(f) Removed noise corresponding to (a)-(c), respectively. (g)-(i) Local similarity comparison corresponding to (a)-(c), respectively.}
\label{fig:npre0,rna-ortho0,rna-ortho20,nprediff0,rnadiff-ortho0,rnadiff-ortho20,rna-simi,rna-simi-ortho,rna-simi-ortho2}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-npre-a}
   \label{fig:zoom-npre-a}}
   \subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-npre-b}
   \label{fig:zoom-npre-b}}\\
\subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rna-ortho-a}
   \label{fig:zoom-rna-ortho-a}}
   \subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rna-ortho2-b}
   \label{fig:zoom-rna-ortho-b}}\\
\subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rna-ortho2-a}
   \label{fig:zoom-rna-ortho2-a}}
   \subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rna-ortho2-b}
   \label{fig:zoom-rna-ortho2-b}}\\  
\caption{Zoomed comparison of denoised sections. Left column: zoomed frame box A. Right column: zoomed frame box B.}
\label{fig:zoom-npre-a,zoom-npre-b,zoom-rna-ortho-a,zoom-rna-ortho-b,zoom-rna-ortho2-a,zoom-rna-ortho2-b}
\end{figure}

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rnadif-a}
   \label{fig:zoom-rnadif-a}}
   \subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-rnadif-b}
   \label{fig:zoom-rnadif-b}}\\
\subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-orthodif-a}
   \label{fig:zoom-orthodif-a}}
   \subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-orthodif-b}
   \label{fig:zoom-orthodif-b}}\\
\subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-ortho2dif-a}
   \label{fig:zoom-ortho2dif-a}}
   \subfloat[]{\includegraphics[width=0.45\columnwidth]{rna/Fig/zoom-ortho2dif-b}
   \label{fig:zoom-ortho2dif-b}}\\  
\caption{Zoomed comparison of noise sections. Left column: zoomed frame box A. Right column: zoomed frame box B.}
\label{fig:zoom-rnadif-a,zoom-rnadif-b,zoom-orthodif-a,zoom-orthodif-b,zoom-ortho2dif-a,zoom-ortho2dif-b}
\end{figure}

@@

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.22\columnwidth]{linear/Fig/c}
   \label{fig:c}}
\subfloat[]{\includegraphics[width=0.22\columnwidth]{linear/Fig/cn}
   \label{fig:cn}}\\
\subfloat[]{\includegraphics[width=0.22\columnwidth]{linear/Fig/c-fx}
   \label{fig:c-fx}}
\subfloat[]{\includegraphics[width=0.22\columnwidth]{linear/Fig/c-fx-n0}
   \label{fig:c-fx-n0}}\\
\subfloat[]{\includegraphics[width=0.22\columnwidth]{linear/Fig/c-fxp}
   \label{fig:c-fxp}}
\subfloat[]{\includegraphics[width=0.22\columnwidth]{linear/Fig/c-fxp-n0}
   \label{fig:c-fxp-n0}}\\   
\subfloat[]{\includegraphics[width=0.22\columnwidth]{linear/Fig/c-fxortho}
   \label{fig:c-fxortho}}
\subfloat[]{\includegraphics[width=0.22\columnwidth]{linear/Fig/c-fxortho-n0}
   \label{fig:c-fxortho-n0}}\\    
\caption{\new{Comparison between the $f-x$ prediction method, $f-x$ projection method, and the hybrid $f-x$ prediction and orthogonalization method. First row: Clean and noisy data. Second row: denoised data and noise section using the $f-x$ prediction method.  Third row: denoised data and noise section using the $f-x$ projection method. Fourth row: denoised data and noise section using the hybrid method.}}
\label{fig:comp}
\end{figure}

@@

\bibliographystyle{seg}
\bibliography{ortho}
